---
title: "VCF2 - Sampling"
author: "Jonathan Karl"
date: '2023-04-19'
output: html_document
---

```{r}
rm(list = ls())

# Prevent scientific notation
knitr::opts_knit$set(options(scipen=999))

# Install and load all the packages that will be used for analysis
pkgs <- c("tidyverse", "sp", "googlesheets4","rgdal", "rgeos", "raster", "sf")

miss_pkgs <- pkgs[!pkgs %in% installed.packages()[,1]] # vector of missing packages
if(length(miss_pkgs)>0){
  install.packages(miss_pkgs)
}
invisible(lapply(pkgs,library,character.only=TRUE))

# Clear our memory by removing objects that are no longer needed.
rm(miss_pkgs, pkgs)
```

```{r}
nairobi <- 4397073
kajiado <- 1117840
kiambu <- 2454504
machakos <- 1421932

total_study_area_pop <- nairobi + kajiado + kiambu + machakos

# The real stuff
recruitment <- 16538
baseline <- 12250
endline <- 8500


# For IRB
recruitment <- 19250
baseline <- 14000
endline <- 10000



# Nairobi
round((nairobi/total_study_area_pop)*recruitment/4) # Recruitment
round((nairobi/total_study_area_pop)*baseline/4) # Baseline
round((nairobi/total_study_area_pop)*endline/4)# Endline

# Kajiado
round((kajiado/total_study_area_pop)*recruitment/4) # Recruitment
round((kajiado/total_study_area_pop)*baseline/4) # Baseline
round((kajiado/total_study_area_pop)*endline/4) # Endline

# Kiambu
round((kiambu/total_study_area_pop)*recruitment/4) # Recruitment
round((kiambu/total_study_area_pop)*baseline/4) # Baseline
round((kiambu/total_study_area_pop)*endline/4) # Endline

# Machakos
round((machakos/total_study_area_pop)*recruitment/4) # Recruitment
round((machakos/total_study_area_pop)*baseline/4) # Baseline
round((machakos/total_study_area_pop)*endline/4) # Endline



# Final sample into clusters - How many clusters per place?
as.matrix(c(nairobi = round((nairobi/total_study_area_pop)*endline)/85,
kajiado = round((kajiado/total_study_area_pop)*endline)/85,
kiambu = round((kiambu/total_study_area_pop)*endline)/85,
machakos = round((machakos/total_study_area_pop)*endline)/85))

```

*From the Paper No margin, no mission? A field experiment on incentives for public service delivery:* To implement the design, we first conducted a census of all hair salons in Lusaka, collecting GPS coordinates and numerous salon and stylist characteristics. We then imposed a grid on the GPS-mapped locations of the salons, to divide the city into equal geographical areas of 650 by 650 m each. We excluded a buffer of 75 m on all sides of the grid cell, resulting in at least 150 m between salons in adjacent areas. The resulting areas, each measuring 250,000 m2, served as the unit of randomization. Salons located in buffer areas were not invited to join the program. The final sample for randomization consists of 205 distinct neighbourhoods, containing 1222 hair salons.

*Jonathan's Approach:* This study is design for urban and peri-urban areas in and around Nairobi. Accordingly, we labelled all wards in Nairobi and surrounding counties (Kiambu, Machakos, Kajiado) with the help of Field Officers as rural, peri-urban and urban. Within the wards labelled as peri-urban and urban, we randomly allocated circular clusters with a 1-mile radius (the minimum geographical targeting area Facebook's advertising ecosystem allows). 


## Read in geo-data and geo-entity labels

```{r}

# Read in Shapefile
shp_kenya_adm3 <- readOGR(dsn = "gadm41_KEN_shp/gadm41_KEN_3.shp")

# Select relevant counties
shp_kenya_adm3 <- shp_kenya_adm3[shp_kenya_adm3$NAME_1 %in% c("Nairobi", "Machakos", "Kajiado", "Kiambu"),]

# Select relevant Wards
labelled_wards <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1NLDeLVP5OXw91kX41BCtgZmZnjIsSZfTBjmXBsSnqFs/edit#gid=1092120316")

# Create final label for wards without disagreement
idx_no_disagreement <- apply(labelled_wards[,4:7], FUN = function(x) length(unique(na.omit(x))) < 2, MARGIN = 1)
labelled_wards$final_label[idx_no_disagreement] <- apply(labelled_wards[idx_no_disagreement,4:7], FUN = function(x) unique(na.omit(x)), MARGIN = 1)

# For those with disagreement, adopt the field verification column
labelled_wards$final_label[!idx_no_disagreement] <- labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Field verification`[!idx_no_disagreement]

# Add the last few in Kiambu
labelled_wards$final_label[!is.na(labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Busara colleagues`)] <- labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Busara colleagues`[!is.na(labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Busara colleagues`)]

# Export Shapefile to view in QGIS for sensechecking output visually
shp_kenya_adm3$geo_entity <- labelled_wards$final_label
writeOGR(shp_kenya_adm3, dsn = 'gadm41_KEN_shp', layer = 'gadm41_KEN_3_urban_rural_classified', driver = "ESRI Shapefile", overwrite_layer = TRUE)

```

## Distribute points

```{r}

# Select only polygons that are urban or peri-urban
shp_kenya_adm3 <- shp_kenya_adm3[shp_kenya_adm3$geo_entity %in% c("urban", "peri-urban"),]

# Define the bounds of the polygon underlying the geospatial object
bounds <- shp_kenya_adm3@polygons[[1]]@Polygons[[1]]@coords

# Define the distance threshold (2 miles in this case)
distance_threshold <- 2 * 1609.34 + 200  # 1 mile = 1609.34 meters + Buffer between Clusters

# Create an empty spatial points object
points <- SpatialPoints(data.frame(x = 0, y = 0), proj4string = CRS(proj4string(shp_kenya_adm3)))[-1,]

# Set a seed
set.seed(92)

# Generate random points until reaching the desired number (100 in this case)
count_points <- 1
count_tries <- 1
while(length(points) < 1000) {
  # Generate a random point within the bounds of the polygon
  random_point <- spsample(shp_kenya_adm3, 1, type = "random", iter=20)
  #print(random_point)
  print(count_tries)
  
  # Check if the new point is at least 2 miles away from existing points
  if(length(points) > 0) {
    distances <- raster::pointDistance(points, random_point, lonlat = T)
    count_tries <- count_tries + 1

    if(min(distances) < distance_threshold) {
      next  # Skip to the next iteration if the minimum distance is less than the threshold
    }
  }
  
  # Add the new point to the points object
  points <- rbind(points, random_point)
  print(paste("New Point:", count_points))
  count_points <- count_points + 1
}

# Plot the points within the polygon
plot(shp_kenya_adm3)
points(points, col = "red", pch = 1)


points_df <- SpatialPointsDataFrame(coords = data.frame(points), data = data.frame(cluster_id = 1:length(points)))
temp <- as(points,"SpatialPointsDataFrame")
writeOGR(obj=points_df, dsn="clusters", layer="points", driver="ESRI Shapefile", overwrite_layer = TRUE) # this is in equal area projection

```

## Select clusters with a population probability weight

```{r}

# How many clusters? (100 necessary for power calculation --> but we will oversample by 16%)
number_clusters <- 116

# Read in Population File (Takes some time...the commented out code crops the file to the study areas and cuts out the rest of Kenya)
#ken_general_2020 <- read.csv("population_density_data/ken_general_2020.csv")
#head(ken_general_2020)
#
## Filter df for the rows within the box of the 4 target counties
#ken_general_2020_cropped <- ken_general_2020 %>% 
#  filter(longitude >= 35.9962005610001370 & longitude <= 37.9374580390000347 & latitude >= -3.1870117179998942 & latitude <= -0.7526243919999729)
#write.csv(ken_general_2020_cropped, "population_density_data/ken_general_2020_cropped.csv")

# Read in the filtered data
ken_general_2020_cropped <- read.csv("population_density_data/ken_general_2020_cropped.csv")

# Convert to sf object
ken_general_2020_cropped_sf <- st_as_sf(ken_general_2020_cropped, coords = c("longitude", "latitude"), crs = 4326)

# Read in cluster points
cluster_choiceset <- readOGR("clusters/points.shp")
crs(cluster_choiceset) <- "+proj=longlat +datum=WGS84 +no_defs"

# Convert to sf data frame
clusters_sf <- st_as_sf(cluster_choiceset)

# Set the radius in meters (1 mile = 1609.34 meters)
radius_meters <- 1609.34

# Create circular polygons with a radius of 1 mile
clusters_circles_sf <- st_buffer(clusters_sf, dist = radius_meters)

# Join clusters and population_points
joined_data <- st_join(ken_general_2020_cropped_sf, clusters_circles_sf, join = st_within)

# Aggregate the sum of the population density for each polygon (cluster)
aggregated_pop_cluster <- aggregate(joined_data$ken_general_2020, list(joined_data$cluster_id), sum)

#### Plot the clusters onto the map with population density and administrative boundaries #####

### To enable the plotting of the pop-density data, convert joined geodata into df and clean it
joined_data_df <- data.frame(joined_data)
joined_data_df$geometry <- as.character(joined_data_df$geometry)
joined_data_df_temp <- joined_data_df %>% 
  separate(geometry, into = c("Longitude", "Latitude"), ",")
joined_data_df_temp$Longitude <- as.numeric(str_remove_all(joined_data_df_temp$Longitude, "c\\("))
joined_data_df_temp$Latitude <- as.numeric(str_remove_all(joined_data_df_temp$Latitude, "\\)"))

# To enable plotting the clusters and their associated population density --> Merge the aggregated population data and the locations of the clusters and select the clusters by population weight
aggregated_pop_cluster <- merge(data.frame(cluster_choiceset), aggregated_pop_cluster, by.x = "cluster_id", by.y = "Group.1")

################ Randomly select clusters with population weights
# Set a seed
set.seed(92)
selected_cluster_ids <- sample(x = aggregated_pop_cluster$cluster_id, prob = aggregated_pop_cluster$x, size = number_clusters, replace = F)

# Read in a Kenya map to enable plotting it.
Kenya_map <- st_read("gadm41_KEN_shp/gadm41_KEN_3_urban_rural_classified.shp")

# PLOT IT
ggplot() +
  geom_sf(data = Kenya_map, color = "black") + 
  geom_point(data = joined_data_df_temp, aes(x = Longitude, y = Latitude, color = ken_general_2020), alpha = 0.1, size = 0.00000001) +
  geom_point(data = aggregated_pop_cluster[aggregated_pop_cluster$cluster_id %in% selected_cluster_ids,], aes(x = coords.x1, y = coords.x2, alpha = x), size = 1.609, color = "orange") +
  scale_color_continuous(type = "viridis") +
  theme_minimal()

# Export clusters to look at them in QGIS
selected_clusters <- clusters_sf[clusters_sf$cluster_id %in% selected_cluster_ids,]
st_write(selected_clusters, "clusters/randomly_selected_clusters.shp", append = F)

```

# Extracting sample size by County

```{r}

# Read in county level geospatial data
Kenya_map_counties <- st_read("gadm41_KEN_shp/gadm41_KEN_1.shp")

# Join county level admin data and the cluster locations
ken_county_cluster_join <- selected_clusters %>% st_join(Kenya_map_counties, join = st_within, left = FALSE) 

# Compute sample sizes by County
table(ken_county_cluster_join$NAME_1)/sum(table(ken_county_cluster_join$NAME_1))

```


# Making recruitment easier for FOs

```{r}

# Which subcounties intersect with each cluster

# Read in clusters + buffer them for 1mile
selected_clusters <- st_read("clusters/randomly_selected_clusters.shp")
selected_clusters_buffered_sf <- st_buffer(selected_clusters, dist = radius_meters)

# Read in county level geospatial data - subcounties
Kenya_map_sub_counties <- st_read("gadm41_KEN_shp/gadm41_KEN_2.shp")

# 
a <- st_intersection(Kenya_map_sub_counties, selected_clusters_buffered_sf) 
b <- st_intersection(selected_clusters_buffered_sf, Kenya_map_sub_counties) 

# Compute area for each intersection
a$area <- st_area(a)

# Compute Endline Sample Size by subcounty
c <- data.frame(a) %>% 
  group_by(NAME_1, NAME_2) %>% 
  summarise(sum_area = sum(area), .groups = "drop") %>% 
  mutate(share_area = as.numeric(sum_area/sum(sum_area))) %>% 
  mutate(sample_size = round(share_area*8500))

# Add the overraching circles to nearby subcounties
c <- c %>% 
  filter(NAME_1 %in% c("Nairobi", "Machakos", "Kiambu", "Kajiado")) 

c[c$NAME_2 == "Mwala",]$sample_size <- c[c$NAME_2 == "Mwala",]$sample_size + 10
c[c$NAME_2 == "Yatta",]$sample_size <- c[c$NAME_2 == "Yatta",]$sample_size + 6
c[c$NAME_2 == "Thika Town",]$sample_size <- c[c$NAME_2 == "Thika Town",]$sample_size + 100
c[c$NAME_2 == "Gatundu North",]$sample_size <- c[c$NAME_2 == "Gatundu North",]$sample_size + 20
c[c$NAME_2 == "Lari",]$sample_size <- c[c$NAME_2 == "Lari",]$sample_size + 60
c[c$NAME_2 == "Lari",]$sample_size <- c[c$NAME_2 == "Lari",]$sample_size + 30


# Compute FOs needed 
c$fo_needed_recruitment <- ((c$sample_size/sum(c$sample_size))*85)

# Export to Gsheets
range_write("https://docs.google.com/spreadsheets/d/1qjiBQzsF3KVVPh0eQH8X3fhCrPaAp-TIUeWC7yNTZ5I/edit#gid=360969076",
            c[,c(1,2,5,6)])



```

