---
title: "VCF2 - Sampling"
author: "Jonathan Karl"
date: '2023-04-19'
output: html_document
---

```{r}
rm(list = ls())

# Prevent scientific notation
knitr::opts_knit$set(options(scipen=999))

# Install and load all the packages that will be used for analysis
pkgs <- c("tidyverse", "sp", "googlesheets4","rgdal", "rgeos", "raster", "sf", "randomizr")

miss_pkgs <- pkgs[!pkgs %in% installed.packages()[,1]] # vector of missing packages
if(length(miss_pkgs)>0){
  install.packages(miss_pkgs)
}
invisible(lapply(pkgs,library,character.only=TRUE))

# Clear our memory by removing objects that are no longer needed.
rm(miss_pkgs, pkgs)
```

*From the Paper No margin, no mission? A field experiment on incentives for public service delivery:* To implement the design, we first conducted a census of all hair salons in Lusaka, collecting GPS coordinates and numerous salon and stylist characteristics. We then imposed a grid on the GPS-mapped locations of the salons, to divide the city into equal geographical areas of 650 by 650 m each. We excluded a buffer of 75 m on all sides of the grid cell, resulting in at least 150 m between salons in adjacent areas. The resulting areas, each measuring 250,000 m2, served as the unit of randomization. Salons located in buffer areas were not invited to join the program. The final sample for randomization consists of 205 distinct neighbourhoods, containing 1222 hair salons.

*Jonathan's Approach:* This study is design for urban and peri-urban areas in and around Nairobi. Accordingly, we labelled all wards in Nairobi and surrounding counties (Kiambu, Machakos, Kajiado) with the help of Field Officers as rural, peri-urban and urban. Within the wards labelled as peri-urban and urban, we randomly allocated circular clusters with a 1-mile radius (the minimum geographical targeting area Facebook's advertising ecosystem allows). 


## Read in geo-data and geo-entity labels

```{r}

# Read in Shapefile
shp_kenya_adm3 <- readOGR(dsn = "gadm41_KEN_shp/gadm41_KEN_3.shp")

# Select relevant counties
shp_kenya_adm3 <- shp_kenya_adm3[shp_kenya_adm3$NAME_1 %in% c("Nairobi", "Machakos", "Kajiado", "Kiambu"),]

# Select relevant Wards
labelled_wards <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1NLDeLVP5OXw91kX41BCtgZmZnjIsSZfTBjmXBsSnqFs/edit#gid=1092120316")

# Create final label for wards without disagreement
idx_no_disagreement <- apply(labelled_wards[,4:7], FUN = function(x) length(unique(na.omit(x))) < 2, MARGIN = 1)
labelled_wards$final_label[idx_no_disagreement] <- apply(labelled_wards[idx_no_disagreement,4:7], FUN = function(x) unique(na.omit(x)), MARGIN = 1)

# For those with disagreement, adopt the field verification column
labelled_wards$final_label[!idx_no_disagreement] <- labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Field verification`[!idx_no_disagreement]

# Add the last few in Kiambu
labelled_wards$final_label[!is.na(labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Busara colleagues`)] <- labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Busara colleagues`[!is.na(labelled_wards$`Not-rural? (i.e. urban / peri-urban) - Busara colleagues`)]

# Export Shapefile to view in QGIS for sensechecking output visually
shp_kenya_adm3$geo_entity <- labelled_wards$final_label
writeOGR(shp_kenya_adm3, dsn = 'gadm41_KEN_shp', layer = 'gadm41_KEN_3_urban_rural_classified', driver = "ESRI Shapefile", overwrite_layer = TRUE)

```

## Distribute points

```{r}

# Select only polygons that are urban or peri-urban
shp_kenya_adm3 <- shp_kenya_adm3[shp_kenya_adm3$geo_entity %in% c("urban", "peri-urban"),]

# Define the bounds of the polygon underlying the geospatial object
bounds <- shp_kenya_adm3@polygons[[1]]@Polygons[[1]]@coords

# Define the distance threshold (2 miles in this case)
distance_threshold <- 2 * 1609.34 + 200  # 1 mile = 1609.34 meters + Buffer between Clusters

# Create an empty spatial points object
points <- SpatialPoints(data.frame(x = 0, y = 0), proj4string = CRS(proj4string(shp_kenya_adm3)))[-1,]

# Set a seed
set.seed(92)

# Generate random points until reaching the desired number (100 in this case)
count_points <- 1
count_tries <- 1
while(length(points) < 1000) {
  # Generate a random point within the bounds of the polygon
  random_point <- spsample(shp_kenya_adm3, 1, type = "random", iter=20)
  #print(random_point)
  print(count_tries)
  
  # Check if the new point is at least 2 miles away from existing points
  if(length(points) > 0) {
    distances <- raster::pointDistance(points, random_point, lonlat = T)
    count_tries <- count_tries + 1

    if(min(distances) < distance_threshold) {
      next  # Skip to the next iteration if the minimum distance is less than the threshold
    }
  }
  
  # Add the new point to the points object
  points <- rbind(points, random_point)
  print(paste("New Point:", count_points))
  count_points <- count_points + 1
}

# Plot the points within the polygon
plot(shp_kenya_adm3)
points(points, col = "red", pch = 1)

# Export
points_df <- SpatialPointsDataFrame(coords = data.frame(points), data = data.frame(cluster_id = 1:length(points)))
temp <- as(points,"SpatialPointsDataFrame")
writeOGR(obj=points_df, dsn="clusters", layer="points", driver="ESRI Shapefile", overwrite_layer = TRUE) # this is in equal area projection

```

## Select clusters with a population probability weight

```{r}

# How many clusters? (100 necessary for power calculation --> but we will oversample by 16%)
number_clusters <- 116

# Read in Population File (Takes some time...the commented out code crops the file to the study areas and cuts out the rest of Kenya)
#ken_general_2020 <- read.csv("population_density_data/ken_general_2020.csv")
#head(ken_general_2020)
#
## Filter df for the rows within the box of the 4 target counties
#ken_general_2020_cropped <- ken_general_2020 %>% 
#  filter(longitude >= 35.9962005610001370 & longitude <= 37.9374580390000347 & latitude >= -3.1870117179998942 & latitude <= -0.7526243919999729)
#write.csv(ken_general_2020_cropped, "population_density_data/ken_general_2020_cropped.csv")

# Read in the filtered data
ken_general_2020_cropped <- read.csv("population_density_data/ken_general_2020_cropped.csv")

# Convert to sf object
ken_general_2020_cropped_sf <- st_as_sf(ken_general_2020_cropped, coords = c("longitude", "latitude"), crs = 4326)

# Read in cluster points
cluster_choiceset <- readOGR("clusters/points.shp")
crs(cluster_choiceset) <- "+proj=longlat +datum=WGS84 +no_defs"

# Convert to sf data frame
clusters_sf <- st_as_sf(cluster_choiceset)

# Set the radius in meters (1 mile = 1609.34 meters)
radius_meters <- 1609.34

# Create circular polygons with a radius of 1 mile
clusters_circles_sf <- st_buffer(clusters_sf, dist = radius_meters)

# Join clusters and population_points
joined_data <- st_join(ken_general_2020_cropped_sf, clusters_circles_sf, join = st_within)

# Aggregate the sum of the population density for each polygon (cluster)
aggregated_pop_cluster <- aggregate(joined_data$ken_general_2020, list(joined_data$cluster_id), sum)

#### Plot the clusters onto the map with population density and administrative boundaries #####

### To enable the plotting of the pop-density data, convert joined geodata into df and clean it
joined_data_df <- data.frame(joined_data)
joined_data_df$geometry <- as.character(joined_data_df$geometry)
joined_data_df_temp <- joined_data_df %>% 
  separate(geometry, into = c("Longitude", "Latitude"), ",")
joined_data_df_temp$Longitude <- as.numeric(str_remove_all(joined_data_df_temp$Longitude, "c\\("))
joined_data_df_temp$Latitude <- as.numeric(str_remove_all(joined_data_df_temp$Latitude, "\\)"))

# To enable plotting the clusters and their associated population density --> Merge the aggregated population data and the locations of the clusters and select the clusters by population weight
aggregated_pop_cluster <- merge(data.frame(cluster_choiceset), aggregated_pop_cluster, by.x = "cluster_id", by.y = "Group.1")

################ Randomly select clusters with population weights
# Set a seed
set.seed(92)

# Sample
selected_cluster_ids <- sample(x = aggregated_pop_cluster$cluster_id, prob = aggregated_pop_cluster$x, size = number_clusters, replace = F)

# Read in a Kenya map to enable plotting it.
Kenya_map <- st_read("gadm41_KEN_shp/gadm41_KEN_3_urban_rural_classified.shp")

# PLOT IT
ggplot() +
  geom_sf(data = Kenya_map, color = "black") + 
  geom_point(data = joined_data_df_temp, aes(x = Longitude, y = Latitude, color = ken_general_2020), alpha = 0.1, size = 0.00000001) +
  geom_point(data = aggregated_pop_cluster[aggregated_pop_cluster$cluster_id %in% selected_cluster_ids,], aes(x = coords.x1, y = coords.x2, alpha = x), size = 1.609, color = "orange") +
  scale_color_continuous(type = "viridis") +
  theme_minimal()

# Export clusters to look at them in QGIS
selected_clusters <- clusters_sf[clusters_sf$cluster_id %in% selected_cluster_ids,]
st_write(selected_clusters, "clusters/randomly_selected_clusters.shp", append = F)

```

# Allocating clusters to Treatment Groups

```{r}

# Read in buffered clusters
selected_buffered_clusters <- st_read("clusters/randomly_selected_clusters_buffered.shp")

# Randomly allocate clusters to treatment groups
set.seed(4)
selected_buffered_clusters$group <- complete_ra(nrow(selected_buffered_clusters), num_arms = 4, conditions = c("Control", "Online_Only", "Offline_Only", "Online_Offline"))

# Export new Shapefile
st_crs(selected_buffered_clusters) <- st_crs(st_read("Raw Data/gadm41_KEN_shp/gadm41_KEN_3_urban_rural_classified.shp"))
st_write(selected_buffered_clusters, "clusters/randomly_selected_clusters_buffered_allocated_to_groups.shp", append = F)

```



# Making recruitment easier for FOs (Sample Sizes by County and Subcounty)

```{r}

# Read in clusters
selected_clusters_buffered_allocated <- st_read("clusters/randomly_selected_clusters_buffered_allocated_to_groups.shp")

# Read in county level geospatial data - subcounties
Kenya_map_sub_counties <- st_read("Raw Data/gadm41_KEN_shp/gadm41_KEN_2.shp")

# Intersect subcounty map with clusters
intersection_subcounty_map_clusters <- st_intersection(Kenya_map_ward_level, selected_clusters_buffered_allocated) 
intersection_subcounty_map_clusters$area <- st_area(intersection_subcounty_map_clusters)

# Compute Endline Sample Size by subcounty
data.frame(intersection_subcounty_map_clusters) %>% 
  group_by(NAME_1, NAME_2) %>% # BIG CONSTRUCTION SITEEEEEEEEEEEEE ONLY FROM 227 TO 235
  summarise(sum_area = sum(area), .groups = "drop") %>% 
  mutate(share_area = as.numeric(sum_area/sum(sum_area))) %>% 
  ungroup() %>% 
  mutate(sample_size_recruitment = )
  mutate(sample_size_endline = round(share_area*8500)) %>% 
  mutate(FOs_needed_endline = (sample_size_endline/sum(sample_size_endline))*67))

# Add the overraching circles to nearby subcounties
c <- c %>% 
  filter(NAME_1 %in% c("Nairobi", "Machakos", "Kiambu", "Kajiado")) 

c[c$NAME_2 == "Mwala",]$sample_size <- c[c$NAME_2 == "Mwala",]$sample_size + 10
c[c$NAME_2 == "Yatta",]$sample_size <- c[c$NAME_2 == "Yatta",]$sample_size + 6
c[c$NAME_2 == "Thika Town",]$sample_size <- c[c$NAME_2 == "Thika Town",]$sample_size + 100
c[c$NAME_2 == "Gatundu North",]$sample_size <- c[c$NAME_2 == "Gatundu North",]$sample_size + 20
c[c$NAME_2 == "Lari",]$sample_size <- c[c$NAME_2 == "Lari",]$sample_size + 60
c[c$NAME_2 == "Lari",]$sample_size <- c[c$NAME_2 == "Lari",]$sample_size + 30

# Compute FOs needed 
c$fo_needed_recruitment_endline <- ((c$sample_size/sum(c$sample_size))*85)

# Export to Gsheets
range_write("https://docs.google.com/spreadsheets/d/1qjiBQzsF3KVVPh0eQH8X3fhCrPaAp-TIUeWC7yNTZ5I/edit#gid=360969076",
            sheet = "FO Needs",
            c[,c(1,2,5,6)])

```

# Export List of Cluster IDs and where they are (+ sample sizes) (also export sample size by county and subcounty)

```{r}

# Read in clusters
selected_clusters_buffered_allocated <- st_read("clusters/randomly_selected_clusters_buffered_allocated_to_groups.shp")

# Read in county level geospatial data - wards
Kenya_map_ward_level <- st_read("Raw Data/gadm41_KEN_shp/gadm41_KEN_3_urban_rural_classified.shp")

# Intersect ward map with clusters
intersection_ward_map_clusters <- st_intersection(Kenya_map_ward_level, selected_clusters_buffered_allocated) 
intersection_ward_map_clusters$area <- st_area(intersection_ward_map_clusters)

# Before computing areas with which the cluster overlaps and the group the cluster is allocated to prep the recruitment discrepancy in sample size for the clusters
recruitment_baseline_samplesize_discrepancy <- c("Control" = 121, "Online_Only" = 121, "Offline_Only" = 143, "Online_Offline" = 143)

intersection_ward_map_clusters_df <- data.frame(intersection_ward_map_clusters) %>% 
  group_by(cluster_id) %>% 
  summarise(group = unique(group), County = toString(unique(NAME_1)), Sub_County = toString(unique(NAME_2)), Ward = toString(unique(NAME_3))) %>%
  ungroup() %>% 
  mutate(sample_size_recruitment_baseline = unname(recruitment_samplesize_discrepancy[group])) %>% 
  mutate(sample_size_endline = 85) %>% 
  arrange(County, Sub_County)
  

# Export to Gsheets
range_write("https://docs.google.com/spreadsheets/d/1qjiBQzsF3KVVPh0eQH8X3fhCrPaAp-TIUeWC7yNTZ5I/edit#gid=360969076",
            sheet = "Clusters Locations & Sample Sizes",
            intersection_ward_map_clusters_df, 
            reformat = F)



# EXPORT Sample size by County and Subcounty
sample_size_county_subcounty <- data.frame(intersection_ward_map_clusters) %>% 
  group_by(NAME_1, NAME_2) %>% 
  summarise() %>%
  ungroup() %>% 
  mutate(sample_size_recruitment = unname(recruitment_samplesize_discrepancy[group])) %>% 
  mutate(sample_size_baseline = 106) %>% 
  mutate(sample_size_endline = 85) %>% 
  arrange(County, Sub_County)
  

# Export to Gsheets
range_write("https://docs.google.com/spreadsheets/d/1qjiBQzsF3KVVPh0eQH8X3fhCrPaAp-TIUeWC7yNTZ5I/edit#gid=360969076",
            sheet = "Clusters Locations & Sample Sizes",
            intersection_ward_map_clusters_df, 
            reformat = F)

```

# Assign responsibility to SFO by Cluster

```{r}

# Read in clusters
selected_clusters_buffered_allocated <- st_read("clusters/randomly_selected_clusters_buffered_allocated_to_groups.shp")

# Read in county level geospatial data
Kenya_map_county_level <- st_read("Raw Data/gadm41_KEN_shp/gadm41_KEN_1.shp")

# Intersect ward map with clusters
intersection_county_map_clusters <- st_intersection(Kenya_map_county_level, selected_clusters_buffered_allocated) 
intersection_county_map_clusters$area <- st_area(intersection_county_map_clusters)

# Compute the majority share by cluster and assign SFOs (highlight clusters that are heavily on the border where the majority is below < 75%)
cluster_bycounty_share <- data.frame(intersection_county_map_clusters) %>% 
  group_by(cluster_id) %>% 
  summarise(NAME_1, share_cluster_area = as.numeric(area/sum(area))) %>% 
  filter(NAME_1 %in% c("Nairobi", "Machakos", "Kajiado", "Kiambu")) %>% 
  filter(share_cluster_area == max(share_cluster_area)) %>% 
  arrange(NAME_1)

fo_assigned_county <- c("Nairobi" = "Martin", "Machakos" = "Billy", "Kajiado" = "Dennis", "Kiambu" = "Naom")
cluster_bycounty_share$sfo_responsible <- unname(fo_assigned_county[cluster_bycounty_share$NAME_1])

# Format into percentages
cluster_bycounty_share$share_cluster_area_percentage <- paste0(round(cluster_bycounty_share$share_cluster_area*100), "%")
cluster_bycounty_share$share_cluster_area <- NULL

# Export to Gsheets
range_write("https://docs.google.com/spreadsheets/d/1qjiBQzsF3KVVPh0eQH8X3fhCrPaAp-TIUeWC7yNTZ5I/edit#gid=360969076",
            sheet = "Clusters Probability of Data Collecton Issues",
            cluster_bycounty_share[,1:3], 
            reformat = F)

```

