---
title: "VCF - HFC - Hairdresser Recruitment"
author: "Jonathan Karl"
date: "2024-02-01"
output: html_document
---

## Setup

```{r}

# Clean the environment
rm(list = ls())

# Prevent scientific notation
knitr::opts_knit$set(options(scipen=999))

# Install and load all the packages that will be used for analysis
pkgs <- c("tidyverse", "googlesheets4", "lubridate", "stringdist", "igraph")

miss_pkgs <- pkgs[!pkgs %in% installed.packages()[,1]] # vector of missing packages
if(length(miss_pkgs)>0){
  install.packages(miss_pkgs)
}
invisible(lapply(pkgs,library,character.only=TRUE))

# Clear our memory by removing objects that are no longer needed.
rm(miss_pkgs, pkgs)
```

## ------Hairdresser Recruitment Data------

### Read Data

```{r}

# Read data
hair_recruit_data <- read.csv("Raw Data/Hairdresser Recruitment/Recruitment Script - Hairdressers V2_WIDE.csv")

# Fix the Stupid Stata ""-issue and Dates
hair_recruit_data[, sapply(hair_recruit_data, class) == 'character'][hair_recruit_data[, sapply(hair_recruit_data, class) == 'character'] == ""] <- NA

# Format dates
hair_recruit_data <- hair_recruit_data %>% 
  mutate_at(c("SubmissionDate","starttime","endtime"), as_datetime, format = "%d.%m.%Y %H:%M:%S")

hair_recruit_data$submission_week <- floor_date(hair_recruit_data$SubmissionDate, "weeks", week_start = 1)
hair_recruit_data$submission_date_dateonly <- floor_date(hair_recruit_data$SubmissionDate, "day")

# Duration and Z scores
hair_recruit_data <- hair_recruit_data %>% mutate(zscore_duration = (duration - mean(duration))/sd(duration))

# Retain only responses where the participant consented
hair_recruit_data <- hair_recruit_data %>% 
  filter(consent_v2 == 1)

# Filter for Main Recruitment
hair_recruit_data <- hair_recruit_data %>% filter(SubmissionDate >= as_datetime("2024-01-25 00:00:00"))

```

### Regular Audio Audits

```{r}
#################### Audit 25 additional surveys per week

# Find out the last date that was uploaded and then filter for dates larger than that.
regular_audits_so_far <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/17sU9kZRTGZQYdCAqtMqpXN6dd7NU-KQ4MHW5tOQDbfM/edit#gid=0",
           sheet = "Regular_Audit_Hair_Recruitment")

set.seed(42)
temp_df2 <- hair_recruit_data %>%
  filter(!is.na(audio)) %>% 
  filter(submission_date_dateonly > max(as_date(regular_audits_so_far$SubmissionDate) + day(1))) %>% 
  mutate(submission_date_dateonly = as.character(submission_date_dateonly)) %>%
  mutate(duration_mins = round(duration/60)) %>% 
  group_by(submission_date_dateonly) %>% 
  slice_sample(n = 5) %>% 
  dplyr::select(final_survey_ID, pull_hairdresser_ID, submission_date_dateonly, duration_mins, en_name, county_name_work, B1_name, audio) # Could add filter for IDs in manul audits

range_write(temp_df2, 
            ss = "https://docs.google.com/spreadsheets/d/17sU9kZRTGZQYdCAqtMqpXN6dd7NU-KQ4MHW5tOQDbfM/edit#gid=0",
            sheet = "Regular_Audit_Hair_Recruitment",
            range = paste0("A",nrow(regular_audits_so_far)+2),
            reformat = F,
            col_names = F)
```

### Merge duplicates in hairdresser database

#### 1. Read Data

##### 1.1 Read and Clean Hairdresser Recruitment Tracker

```{r}

# Read hairdresser recruitment tracker
hair_recruitment_tracker <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1ydO5FV0WPT0nsDh6kEWF32_TIP9KtX1qAUGc7DTOHSU/edit#gid=0", 
           sheet = "Hairdressers_List")

#hair_recruitment_tracker %>% group_by(`Survey Status`) %>% summarise(n = n())

# Filter for the Duplicates
filter_vec <- !is.na(hair_recruitment_tracker$Comment) & hair_recruitment_tracker$`Survey Status` == "Duplicate(Appear more than once)" & !is.na(hair_recruitment_tracker$`Survey Status`)
duplicates_comments <- hair_recruitment_tracker$Comment[filter_vec]
duplicates_original_IDs <- hair_recruitment_tracker$hairdresser_ID[filter_vec]

# Name the vector by the original ID
names(duplicates_comments) <- duplicates_original_IDs
unname(duplicates_comments) # Print it to look at it manually

# Extract the IDs that are specified to be duplicated
duplicate_ids_proxy <- str_extract_all(duplicates_comments, "[0-9]{1,4}[A-Z]{1}[0-9]{1}")
names(duplicate_ids_proxy) <- duplicates_original_IDs

# Check if there is any comments of duplicates where you can't find any IDs?
duplicate_comments_empty <- sapply(duplicate_ids_proxy, length) == 0
if(sum(duplicate_comments_empty) != 0){
  print("Some comments of duplicate hairdresser don't specify which hairdressers they are duplicates of. See below:")
  duplicates_original_IDs[duplicate_comments_empty]
} else { print("There is an ID found in every comment.") }

share_ids_real <- mean(unlist(duplicate_ids_proxy) %in% hair_recruitment_tracker$hairdresser_ID)
if(share_ids_real != 1){
  print("Not all IDs in the comments are real IDs. See below: ")
  unlist(duplicate_ids_proxy)[!(unlist(duplicate_ids_proxy) %in% hair_recruitment_tracker$hairdresser_ID)]
} else { print("All IDs in the comments are real.") }


```

##### 1.2 Read hairdresser database

```{r}

# Read data
hairdresser_database_v1 <- read.csv("Data Exports/vcf2_hairdresser_database_v1.csv")

```

#### 2. Network Analysis

##### 2.1 Verfiy that the duplicates are exhaustively documented

```{r}

# Set up Network
network_matrix <- matrix(data = 0, nrow = nrow(hair_recruitment_tracker), ncol = nrow(hair_recruitment_tracker), dimnames = list(row_names = hair_recruitment_tracker$hairdresser_ID, col_names = hair_recruitment_tracker$hairdresser_ID))
for(i in names(duplicate_ids_proxy)){
  network_matrix[i,duplicate_ids_proxy[[i]]] <- 1
}

# Create the actual network
hairdresser_network <- graph.adjacency(network_matrix, mode = "undirected")
V(hairdresser_network)$hairdresser_ID <- hair_recruitment_tracker$hairdresser_ID
V(hairdresser_network)$hairdresser_name <- hair_recruitment_tracker$B13_hairdressername
V(hairdresser_network)$hairdresser_nickname <- hair_recruitment_tracker$B13_hairdresser_nickname
V(hairdresser_network)$hairdresser_directions <- hair_recruitment_tracker$B14_hairdresserlocation
V(hairdresser_network)$hairdresser_phone <- hair_recruitment_tracker$B11a_phonenumber
V(hairdresser_network)$cluster_ID <- hair_recruitment_tracker$cluster_ID

# Find vertices with a degree greater than 0
v_subset <-  degree(hairdresser_network) > 0
# Subset the network
hairdresser_network_subset <- induced_subgraph(hairdresser_network, which(v_subset))

# Find the connected components
components <- components(hairdresser_network_subset)

# Number of components
n_components <- length(components$membership)

google_df <- data.frame()
for (i in 1:max(components$membership)) {
    # Extract the subgraph corresponding to the ith component
    subgraph <- induced_subgraph(hairdresser_network_subset, which(components$membership == i))
    
    # Number of vertices in the component
    num_vertices <- vcount(subgraph)
    
    # Number of edges that a complete graph would have
    num_edges_complete_graph <- num_vertices * (num_vertices - 1) / 2
    
    # Check if the number of edges in the component equals that of a complete graph
    if (ecount(subgraph) == num_edges_complete_graph) {
      print(paste("Component", i, "is a complete graph."))
    } else {
      print(paste("Component", i, "is an incomplete graph."))
      
      google_df_new <- data.frame(Component = i,
                                  IDs = paste0(names(V(subgraph)), collapse = ", "),
                                  Info = paste0(names(V(subgraph)), " -- Phone: ", V(subgraph)$hairdresser_phone, "\n",
                                                "Name: ", V(subgraph)$hairdresser_name, " -- ", 
                                                "Nickname: ", V(subgraph)$hairdresser_nickname, "\n",
                                                "Cluster_ID: ", V(subgraph)$cluster_ID, " -- ",
                                                "Directions: ", V(subgraph)$hairdresser_directions, "\n\n",
                                                collapse = ""))
      google_df <- rbind(google_df, google_df_new)

      plot(main = paste("Component", i), subgraph, edge.width = 0.5,  vertex.size = degree(subgraph),  vertex.label.cex = 1)
    }
}

# It only makes sense to do this once all hairdressers were visited
range_clear(ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=200599833",
            sheet = "Network_Analysis - Post-Recruitment",
            range = "A2:H1000")

range_write(google_df,
                  ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=200599833",
                  sheet = "Network_Analysis - Post-Recruitment",
                  range = "A2",
                  reformat = F,
                  col_names = F)

```

##### 2.2 Extract which hairdresser ID to merge the matches into

###### 2.2.0 Any merging issues? 

This could be because there is more than 1 non-"duplicate" like "complete" or "ineligible" in the network.

```{r}

all_checks <- NULL
for (i in 1:max(components$membership)) {
    # Extract the subgraph corresponding to the ith component
    subgraph <- induced_subgraph(hairdresser_network_subset, which(components$membership == i))
    
    # Is there more than 1 non-"duplicate" label in the component
    x <- table(hair_recruitment_tracker$`Survey Status`[hair_recruitment_tracker$hairdresser_ID %in% V(subgraph)$name])
    sum_non_duplicate <- sum(x[names(x) != "Duplicate(Appear more than once)"])
    check <- sum_non_duplicate <= 1 & sum_non_duplicate > 0
    
    if(!check){
      print(x)
      print(components$membership[components$membership == i])
    }
    
    all_checks <- c(all_checks, check)
}

table(all_checks)
which(!all_checks)

#components$membership[components$membership == 175]

######## Any single vertex components?
sum(components$csize == 1) # ---> Should be 0

```

###### 2.2.1 Identify complete/incomplete components

```{r}

components_completeness <- NULL
for (i in 1:max(components$membership)) {
    # Extract the subgraph corresponding to the ith component
    subgraph <- induced_subgraph(hairdresser_network_subset, which(components$membership == i))
    
    # Number of vertices in the component
    num_vertices <- vcount(subgraph)
    
    # Number of edges that a complete graph would have
    num_edges_complete_graph <- num_vertices * (num_vertices - 1) / 2
    
    # Check if the number of edges in the component equals that of a complete graph
    if (ecount(subgraph) == num_edges_complete_graph) {
      components_completeness <- c(components_completeness, "Complete")
    } else {
      components_completeness <- c(components_completeness, "Incomplete")
    }
}

```

###### 2.2.2 Prep Helper Functions for Merging Process


```{r}

# Helper Function to reformat the merged information columns on the hairdressers
combine_vectors_hair <- function(original_vector){
  
  # Ensure it's properly pasted
  original_vector <- unlist(str_split(original_vector, ", "))
  
  if(all(original_vector == " ()", na.rm = T)){
    return(NA)
  }
  
  # Remove the empty bits
  original_vector <- original_vector[original_vector != " ()"]

  # Split the names and numbers
  split_data <- str_split(original_vector, " \\(")
  names <- sapply(split_data, `[`, 1)
  numbers <- as.numeric(sapply(split_data, function(x) sub("\\)", "", x[2])))
  
  # Combine the names and their respective sums
  combined_data <- data.frame(name = names, number = numbers) %>%
  group_by(name) %>%
  summarise(number = sum(number))
  
  # Construct the new vector
  new_vector <- paste0(paste(combined_data$name, " (", combined_data$number, ")", sep=""), collapse = ", ")
  
  # Return the result
  return(new_vector)
}

```

##### 2.3 Merge complete components

```{r}

# Which components are complete?
complete_components <- which(components_completeness == "Complete")

# Merge the vertices in the components into the ID that is != "Duplicate"
for(i in complete_components){
  print(i)
  vertices <- names(components$membership[components$membership == i])
  
  merge_destination <- hair_recruitment_tracker$hairdresser_ID[hair_recruitment_tracker$`Survey Status` != "Duplicate(Appear more than once)" & hair_recruitment_tracker$hairdresser_ID %in% vertices]
  
  hair_recruitment_tracker$`Survey Status`[hair_recruitment_tracker$hairdresser_ID %in% vertices]
  
  hair_recruitment_tracker$hairdresser_ID[ hair_recruitment_tracker$hairdresser_ID %in% vertices]
  
  if(length(merge_destination) != 1){
    print("ERROR!")
    break
  }
  
  temp_df <- hairdresser_database_v1[hairdresser_database_v1$hairdresser_ID %in% vertices,]
  
  new_row <- c("hairdresser_ID" = merge_destination, 
               "response_final_IDs" = paste0(temp_df$response_final_IDs, collapse = ", "),
               "treatment_group" = combine_vectors_hair(temp_df$treatment_group),
               "county_name" = combine_vectors_hair(temp_df$county_name),
               "customers_per_hairdresser" = sum(as.integer(temp_df$customers_per_hairdresser)),
               "cluster_ID" = combine_vectors_hair(temp_df$cluster_ID),
               "caregiver_sample_size_in_cluster" = names(which.max(table(temp_df$caregiver_sample_size_in_cluster))),
               "B11a_phonenumber" = combine_vectors_hair(temp_df$B11a_phonenumber),
               "hairdresser_alternative_phonenumber" = combine_vectors_hair(temp_df$hairdresser_alternative_phonenumber),
               "who_does_alternative_phone_belong" = combine_vectors_hair(temp_df$who_does_alternative_phone_belong),
               "B13_hairdressername" = paste0(temp_df$B13_hairdressername, collapse = ", "),
               "B13_hairdresser_nickname" = paste0(temp_df$B13_hairdresser_nickname, collapse = ", "),
               "B14_hairdresserlocation" = paste0(temp_df$B14_hairdresserlocation, collapse = ", "))
  
  # Remove original rows and add the new row
  hairdresser_database_v1 <- hairdresser_database_v1 %>% 
    filter(!(hairdresser_ID %in% vertices)) %>% 
    rbind(new_row)
}

```

##### 2.4 Merge incomplete components

```{r}

# Match the hairdressers without phone numbers either to each other or to hairdressers with phone numbers
matching_hairdressers_network_analysis <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=2120687644",
           sheet = "Network_Analysis - Post-Recruitment")

# Which components are complete?
incomplete_components <- which(components_completeness == "Incomplete")

# Are all incomplete components represented in the network analysis sheet?
test_vec <- mean(incomplete_components %in% matching_hairdressers_network_analysis$`Incomplete Component`)
if(test_vec == 1){
  print("Check, all good!")
} else { print("Something is wrong!") }


# Merge the vertices in the components into the ID that is != "Duplicate"
for(i in incomplete_components){
  
  vertices <- names(components$membership[components$membership == i])
  
  merge_destination <- hair_recruitment_tracker$hairdresser_ID[hair_recruitment_tracker$`Survey Status` != "Duplicate(Appear more than once)" & hair_recruitment_tracker$hairdresser_ID %in% vertices]
  
  if(length(merge_destination) > 1){
    print("ERROR!")
    break
  }
  
  hair_recruitment_tracker[hair_recruitment_tracker$hairdresser_ID %in% vertices,]
  
  temp_df <- hairdresser_database_v1[hairdresser_database_v1$hairdresser_ID %in% vertices,]
  
  new_row <- c("hairdresser_ID" = merge_destination, 
               "response_final_IDs" = paste0(temp_df$response_final_IDs, collapse = ", "),
               "treatment_group" = combine_vectors_hair(temp_df$treatment_group),
               "county_name" = combine_vectors_hair(temp_df$county_name),
               "customers_per_hairdresser" = sum(as.integer(temp_df$customers_per_hairdresser)),
               "cluster_ID" = combine_vectors_hair(temp_df$cluster_ID),
               "caregiver_sample_size_in_cluster" = names(which.max(table(temp_df$caregiver_sample_size_in_cluster))),
               "B11a_phonenumber" = combine_vectors_hair(temp_df$B11a_phonenumber),
               "hairdresser_alternative_phonenumber" = combine_vectors_hair(temp_df$hairdresser_alternative_phonenumber),
               "who_does_alternative_phone_belong" = combine_vectors_hair(temp_df$who_does_alternative_phone_belong),
               "B13_hairdressername" = paste0(temp_df$B13_hairdressername, collapse = ", "),
               "B13_hairdresser_nickname" = paste0(temp_df$B13_hairdresser_nickname, collapse = ", "),
               "B14_hairdresserlocation" = paste0(temp_df$B14_hairdresserlocation, collapse = ", "))
  
  # Remove original rows and add the new row
  hairdresser_database_v1 <- hairdresser_database_v1 %>% 
    filter(!(hairdresser_ID %in% vertices)) %>% 
    rbind(new_row)
  
}

```

