---
title: "VCF_Baseline_Cleaning"
author: "Jonathan Karl"
date: "2024-01-09"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---

## Setup

```{r}
rm(list = ls())

# Prevent scientific notation
knitr::opts_knit$set(options(scipen=999))

# Install and load all the packages that will be used for analysis
pkgs <- c("tidyverse", "googlesheets4", "lubridate", "stringdist")

miss_pkgs <- pkgs[!pkgs %in% installed.packages()[,1]] # vector of missing packages
if(length(miss_pkgs)>0){
  install.packages(miss_pkgs)
}
invisible(lapply(pkgs,library,character.only=TRUE))

# Clear our memory by removing objects that are no longer needed.
rm(miss_pkgs, pkgs)
```

## Read Survey Data

```{r}

# Read data
baseline_data <- read.csv("Raw Data/Main Data Collection/VCF2 - RCT - Recruitment + Baseline - Caregivers_WIDE.csv")

# Fix the Stupid Stata ""-issue and Dates
baseline_data[, sapply(baseline_data, class) == 'character'][baseline_data[, sapply(baseline_data, class) == 'character'] == ""] <- NA

# Format dates
baseline_data <- baseline_data %>% 
  mutate_at(c("SubmissionDate","starttime","endtime"), as_datetime, format = "%d.%m.%Y %H:%M:%S")

baseline_data$submission_week <- floor_date(baseline_data$SubmissionDate, "weeks", week_start = 1)
baseline_data$submission_date_dateonly <- floor_date(baseline_data$SubmissionDate, "day")

# Duration and Z scores
baseline_data <- baseline_data %>% mutate(zscore_duration = (duration - mean(duration))/sd(duration))

# Retain only responses where the participant consented
baseline_data <- baseline_data %>% 
  filter(consent == 1)

# Filter for FO Training
# baseline_data <- baseline_data %>% filter(SubmissionDate >= as_datetime("2023-10-17 14:00:00") & SubmissionDate < as_datetime("2023-10-20 00:00:00"))

# Filter for RCT Pilots
#baseline_data <- baseline_data %>% filter(SubmissionDate > as_datetime("2023-10-20 00:00:00"))

# Filter for Main Data Collection
baseline_data <- baseline_data %>% filter(SubmissionDate > as_datetime("2023-10-24 00:00:00"))

# Filter all cluster 271 responses before 8th November (we are moving this cluster far)
baseline_data <- baseline_data %>% filter(!(SubmissionDate < as_datetime("2023-11-08 00:00:00") & B0_cluster == 271))

# Abandon Clusters
baseline_data <- baseline_data %>% filter(B0_cluster != 197)
baseline_data <- baseline_data %>% filter(B0_cluster != 37)
baseline_data <- baseline_data %>% filter(B0_cluster != 186)
baseline_data <- baseline_data %>% filter(B0_cluster != 414)
baseline_data <- baseline_data %>% filter(B0_cluster != 141)
baseline_data <- baseline_data %>% filter(B0_cluster != 10)
baseline_data <- baseline_data %>% filter(B0_cluster != 363)
baseline_data <- baseline_data %>% filter(B0_cluster != 54)
baseline_data <- baseline_data %>% filter(B0_cluster != 378)
baseline_data <- baseline_data %>% filter(B0_cluster != 248)

```

## Re-Organise Variables

### 1. Clean the randomised questions

```{r}

################### Discernment

# Coalesce the truth discernment columns
for(i in 1:16){
  baseline_data[paste0("truth_discernment_",i)] <- do.call(coalesce, baseline_data[,paste0("truth_discernment_", i, "_set",1:5)])
}

# Drop the truth discernment columns
old_discernment_var_names <- apply(expand.grid("truth_discernment_",1:16,"_set",1:5), 1, paste0, collapse="")
old_discernment_var_names <- str_remove_all(old_discernment_var_names, " ")
baseline_data[old_discernment_var_names] <- NULL

################### Manipulation

# First ensure all the multi-select variable are character variables
multi_select_manip_var_names <- apply(expand.grid("detect_misinfo_",1:12, "_2_set",1:5), 1, paste0, collapse="")
multi_select_manip_var_names <- str_remove_all(multi_select_manip_var_names, " ")
baseline_data[,multi_select_manip_var_names] <- data.frame(lapply(baseline_data[,multi_select_manip_var_names], as.character))

# Coalesce the manipulation columns
for(i in 1:12){
  
  # Is this manipulative?
  baseline_data[paste0("detect_misinfo_",i,"_1")] <- do.call(coalesce, baseline_data[,paste0("detect_misinfo_", i, "_1_set",1:5)])
  
  # Which techniques?
  baseline_data[paste0("detect_misinfo_",i, "_2")] <- do.call(coalesce, baseline_data[,paste0("detect_misinfo_", i, "_2_set",1:5)])
  
  # How confident?
  baseline_data[paste0("detect_misinfo_",i, "_3")] <- do.call(coalesce, baseline_data[,paste0("detect_misinfo_", i, "_3_set",1:5)])
  
  # Would you share?
  baseline_data[paste0("detect_misinfo_",i, "_4")] <- do.call(coalesce, baseline_data[,paste0("detect_misinfo_", i, "_4_set",1:5)])
  
  for(multi in c(1:6,88)){
   
    # Technique multiple select variable
    baseline_data[paste0("detect_misinfo_",i,"_2_",multi)] <- do.call(coalesce, baseline_data[,paste0("detect_misinfo_", i, "_2_set",1:5, "_", multi)])
     
  }
}

# Drop the truth discernment columns
old_manipulation_var_names_1 <- apply(expand.grid("detect_misinfo_",1:12, "_", 1:4, "_set",1:5), 1, paste0, collapse="")
old_manipulation_var_names_1 <- str_remove_all(old_manipulation_var_names_1, " ")
old_manipulation_var_names_2 <- apply(expand.grid("detect_misinfo_",1:12, "_2_set",1:5, "_", c(1:6,88)), 1, paste0, collapse="")
old_manipulation_var_names_2 <- str_remove_all(old_manipulation_var_names_2, " ")
old_manipulation_var_names <- c(old_manipulation_var_names_1, old_manipulation_var_names_2)
baseline_data[old_manipulation_var_names] <- NULL

```

## Filter Data

### 1. Correct survey versions

```{r}

# For the Training Simulation the correct version was 2310171533
# For the main data collection, the minimum acceptable version was 2310231825
# From the 28th October, respondents should use 2310271446
# From the 16th onwards everyone has to use the version 2311151046
# From the 17th onwards everyone has to use the version 2311161331
# From the 25th onwards everyone has to use the version 2311251219

# Filter out wrong versions
baseline_data <- baseline_data %>% 
  filter(formdef_version >= 2310231825)

```

### 2. Eligibility Criteria

Look at those who answered the first question in the baseline and check if they are actually eligible.
If they are not, there is an error in the survey.

**Recruitment Criteria:** 1.
Male or female participants aged 18 years and over 2.
Is the primary caregiver to a daughter between the ages of 10 and 14.
3.
Must have lived in the area for over one (1) year.
4.
Owns their own private smartphone.
5.
Has and uses a Facebook account.
6.
Is willing and able to participate in the survey.
7.
Willing to provide contact information on their hairdresser 8.
Is not a hairdresser 9.
Doesn't live in the same household with a hairdresser

```{r}

eligible <- baseline_data$B3_age != 1 & # Age
  apply(baseline_data[,paste0("between_10_14_",1:max(baseline_data$B6_childnu_count, na.rm = T))] > 0, MARGIN = 1, FUN = function(i) any(i)) & # Female daughter between 10 - 14
  baseline_data$B5_long == 2 & # lived there longer than 1 year
  baseline_data$B7_smartphone == 1 & # Owns smartphone
  baseline_data$B7_shared == 2 & # owns it privately
  baseline_data$B8_socialmedia == 1 & # uses social media
  baseline_data$B8a_whichone_1 == 1 & # uses Facebook
  #### OCCUPATION & LIVING WITH HAIRDRESSER
  baseline_data$consent_hairdresser == 1 & # consent to share contact of hairdresser
  baseline_data$B16_hairdresser_confidence_check == 1 # Are we confident we can recruit this hairdresser?

eligible[is.na(eligible)] <- FALSE # Fix NAs

# Did anyone respond to the first baseline survey question that was not eligible? --? SHOULD BE FALSE
any(!is.na(baseline_data$income_month) & !eligible)

# Filter
baseline_data <- baseline_data[eligible,] 

```

### 3. Unique SurveyID

```{r}

# Should be 0 - anything above 0 indicates there is a surveyID missing
sum(is.na(baseline_data$final_ID))

# Should be 0 - anything above 0 means there is a duplicate surveyID
sum(duplicated(baseline_data$final_ID))

# Delete buggy duplicate responses (delete the first)
baseline_data <- baseline_data[-which(baseline_data$final_ID == "15174Oct28132521")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "97180Oct30171347")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "66112Oct26162143")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "90113Oct24161649")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "93125Oct24142732")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "93118Oct24130037")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "96160Oct24111451")[1],]
baseline_data <- baseline_data[-which(baseline_data$final_ID == "71172Nov13134137")[1],]

# Should be 0 - anything above 0 means there is a duplicate surveyID
sum(duplicated(baseline_data$final_ID))

```

## Manually edit data

### 1. Mislabelled Clusters

```{r}

relabel_clusters <- function(finalids, correct_cluster){
  
  # What is the clusters treatment group 
  correct_cluster_treatment_group <- unique(baseline_data$cluster_treatment_group[baseline_data$B0_cluster == correct_cluster])
  
  # Adjust clusterID
  baseline_data[baseline_data$final_ID %in% finalids, ]$B0_cluster <<- correct_cluster
  
  if(length(correct_cluster_treatment_group) > 1){
    print("ERROR")
  }
  
  # Adjust treatment group
  baseline_data[baseline_data$final_ID %in% finalids, ]$cluster_treatment_group <<- correct_cluster_treatment_group
}



relabel_clusters(c("98197Dec9171002", "76186Dec9123254", "77103Dec9105523", "84166Dec9134533", "13193Dec9154005", "44173Dec9144909", "20185Dec8174959", "77181Dec8164121", "38171Dec8154903", "42152Dec8133125", "44147Dec8114606", "39177Dec9113313"), 428)

relabel_clusters(c("29187Nov29101906"), 128)

relabel_clusters(c("63200Oct30121711", "29166Nov3090457", "69154Oct30154755"), 230)

relabel_clusters(c("66183Nov8160224"), 280)

relabel_clusters(c("63130Nov24165008"), 364)

relabel_clusters(c("77166Dec7104701"), 103)

relabel_clusters(c("102177Oct28132949", "70115Oct28164915"), 318)

relabel_clusters(c("74106Dec13163729"), 318)

relabel_clusters(c("20162Oct24145318"), 207)

relabel_clusters(c("84165Nov23100932"), 403)

relabel_clusters(c("72127Oct26150254", "89150Oct26160443"), 215)

relabel_clusters(c("81161Nov16102342", "52162Nov16113233", "22111Nov16130039", "59133Nov16141055"), 239)

relabel_clusters(c("28141Nov16130304", "104102Nov18143305", "63125Nov18155500", "35187Nov18165511", "27131Nov16101344", "15134Nov16170730"), 218)

relabel_clusters(c("61139Nov23144905"), 282)

relabel_clusters(c("67105Dec15104756", "64199Nov1141133"), 97)

#c("39177Dec9113313") %in% baseline_data$final_ID
```

### 2. Remove Fradulent Data

```{r}
table(baseline_data[baseline_data$en_name == "Ruth Wanjiru Ndungu",]$B0_cluster)

baseline_data %>% 
  group_by(B0_cluster) %>% 
  summarise(n = n()) %>% 
  arrange(B0_cluster)
```

### 3. Manually adjust FO mistakes

```{r}

# 20th Nov, Shanice Linah accidentally keyed in Kiambu as a location instead of Nairobi to the respondent named Lucy Nyamoita
baseline_data[baseline_data$final_ID %in% c("24170Nov20092513"), ]$county_name <- "Nairobi"
baseline_data[baseline_data$final_ID %in% c("24170Nov20092513"), ]$county_name_fo_location <- "Nairobi"

```

### 4. Update new Hairdresser Information acquired post survey

```{r}

# Read sheet with updated information
hairdresser_additional_info <- read_sheet("https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=0", sheet = "Enough Info to Recruit?")

# Which columns are to be updated
update_columns <- c("Hairdresser Phone Number", "More detailed Name", "More detailed Nickname", "More detailed Directions")

# Which rows contain additional information
additional_info_idx <- rowSums(is.na(hairdresser_additional_info[,update_columns])) != ncol(hairdresser_additional_info[,update_columns])

# Update the information
for(i in hairdresser_additional_info[additional_info_idx,]$final_ID){
  
  # Update Phone Number
  if(!is.na(hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`Hairdresser Phone Number`)){
    
    baseline_data[baseline_data$final_ID == i,]$B11a_phonenumber <- hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`Hairdresser Phone Number`
    
  } else {
    next
  }
  
  # Update Name
  if(!is.na(hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`More detailed Name`)){
    
    baseline_data[baseline_data$final_ID == i,]$B13_hairdressername <- paste(baseline_data[baseline_data$final_ID == i,]$B13_hairdressername,
        "-------------------- Additional Information:",
        hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`More detailed Name`)
    
  } else {
    next
  }
  
  # Update Nickname
  if(!is.na(hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`More detailed Nickname`)){
    
    baseline_data[baseline_data$final_ID == i,]$B13_hairdresser_nickname <- paste(baseline_data[baseline_data$final_ID == i,]$B13_hairdresser_nickname,
        "-------------------- Additional Information:",
        hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`More detailed Nickname`)
    
  } else {
    next
  }
  
  # Update Location
  baseline_data[baseline_data$final_ID == i,]$B14_hairdresserlocation <- paste(baseline_data[baseline_data$final_ID == i,]$B14_hairdresserlocation,
        "-------------------- Additional Information:",
        hairdresser_additional_info[hairdresser_additional_info$final_ID == i,]$`More detailed Directions`)
  
}

```

### 5. Secondary Phone Number Unification

--\> Ensuring every unique secondary phone number is matched to only 1 primary phone number

```{r}


# Which primary phone numbers appear more than once
primary_phoneno_freq <- table(baseline_data$B11a_phonenumber) > 1
multi_phoneno <- as.numeric(names(primary_phoneno_freq[primary_phoneno_freq]))
count <- 1

# TAKING THE ALTERNATIVE PHONE NUMBER OUT OF THE GAME
for(i in unique(baseline_data$B11a_phonenumber[baseline_data$B11a_phonenumber %in% multi_phoneno])){
  
  if(all(is.na(baseline_data$B12a_alternativepn[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)]))){
    next
  }
  
  if(length(unique(baseline_data$B12a_alternativepn[baseline_data$B11a_phonenumber == i])) > 1) {
    print(paste0("Count: ",count, " ----- Primary: ", i," Discrepancy: ", paste(baseline_data$B12a_alternativepn[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")))
    
    x <- baseline_data$B12a_alternativepn[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)]
    for(i in unique(x[!is.na(x)])){
      alternative_phonenumber_somewhereelse <- sum(baseline_data$B12a_alternativepn == i, na.rm = T) != sum(x[!is.na(x)] == i)
      if(alternative_phonenumber_somewhereelse){
        
        unique(baseline_data$B11a_phonenumber[which(baseline_data$B12a_alternativepn == i)])
        
        print(paste(i, "ALSO FOUND SOMEWHERE ELSE --- ", paste0(unique(baseline_data$B11a_phonenumber[which(baseline_data$B12a_alternativepn == i)]), collapse = ", ")))}
    }
  
    } else {
    print(paste0("Count: ",count, "<>: ", baseline_data$B12a_alternativepn[baseline_data$B11a_phonenumber == i]))
    }
  count <- count+1
}

```

```{r}

# Adjust alternative phone numbers

# This one was just a typo. It was supposed to be 769145547 but the FO typed 769145541
baseline_data$B11a_phonenumber[baseline_data$B11a_phonenumber == "769145541" & !is.na(baseline_data$B11a_phonenumber)] <- 769145547

# This hairdresser appears to have 3 phone numbers. This is unified to enable easier matching where the first phone number is unified. (The third number is added to the location to retain the information)
baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == "725524368" & !is.na(baseline_data$B11a_phonenumber)] <- paste0(baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == "725524368" & !is.na(baseline_data$B11a_phonenumber)], " --------- additional phonenumber: 725524368")
baseline_data$B11a_phonenumber[baseline_data$B11a_phonenumber == "725524368" & !is.na(baseline_data$B11a_phonenumber)] <- 705764995

```


```{r}

baseline_data %>% 
  filter(cluster_treatment_group %in% c("Offline_Only", "Online_Offline")) %>% 
  filter(county_name == "Nairobi") %>% 
  group_by(B11a_phonenumber) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n))


baseline_data$B13_hairdressername[baseline_data$B11a_phonenumber == 723597681 & !is.na(baseline_data$B11a_phonenumber)]
baseline_data$B13_hairdresser_nickname[baseline_data$B11a_phonenumber == 723597681 & !is.na(baseline_data$B11a_phonenumber)]
baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == 723597681 & !is.na(baseline_data$B11a_phonenumber)]

baseline_data$B13_hairdressername[baseline_data$B11a_phonenumber == 712831038 & !is.na(baseline_data$B11a_phonenumber)]
baseline_data$B13_hairdresser_nickname[baseline_data$B11a_phonenumber == 712831038 & !is.na(baseline_data$B11a_phonenumber)]
baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == 712831038 & !is.na(baseline_data$B11a_phonenumber)]

baseline_data$B13_hairdressername[baseline_data$B11a_phonenumber == 722888318 & !is.na(baseline_data$B11a_phonenumber)]
baseline_data$B13_hairdresser_nickname[baseline_data$B11a_phonenumber == 722888318 & !is.na(baseline_data$B11a_phonenumber)]
baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == 722888318 & !is.na(baseline_data$B11a_phonenumber)]



```


### 6. Detecting Typos in Phone Numbers

```{r}

primary_phone_numbers <- baseline_data$B11a_phonenumber[!is.na(baseline_data$B11a_phonenumber)]
unique_primary_phone_numbers <- unique(baseline_data$B11a_phonenumber[!is.na(baseline_data$B11a_phonenumber)])
count <- 1
suspected_typos_df <- data.frame()

for(i in unique_primary_phone_numbers){
  lv_dist <- stringdist(i, unique_primary_phone_numbers, method = 'lv')
  
  if(sum(lv_dist < 3 & lv_dist > 0) > 0){
    
    # Collect Data on the Source
    freq_source <- sum(i == primary_phone_numbers)
    cluster_id_source <- paste(baseline_data$B0_cluster[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
    hairdresser_name_source <- paste(baseline_data$B13_hairdressername[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
    hairdresser_nickname_source <- paste(baseline_data$B13_hairdresser_nickname[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
    hairdresser_location <- paste(baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)], collapse = "\n")
    final_ids_source <- paste(baseline_data$final_ID[baseline_data$B11a_phonenumber == i & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
    
    # Collect Data on the Proximal Phone Numbers
    phone_numbers_proximity <- lv_dist[lv_dist < 3 & lv_dist > 0]
    proximal_phone_numbers <- unique_primary_phone_numbers[lv_dist < 3 & lv_dist > 0]
    freq_proximal <- table(primary_phone_numbers[primary_phone_numbers %in% proximal_phone_numbers])
    freq_proximal <- freq_proximal[match(proximal_phone_numbers, names(freq_proximal))]
    
    #print(paste0("Count (", count, ") -- Source (n=",freq_source,"): ", i, " ----Proximal Phone Number: ", paste0(names(freq_proximal), " (n=", freq_proximal, "): Distance", "(", phone_numbers_proximity, ")", collapse = " || ")))
    count <- count + 1
    
    count_2 <- 1
    for(j in proximal_phone_numbers){
      cluster_id_proximal <- paste(baseline_data$B0_cluster[baseline_data$B11a_phonenumber == j & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
      hairdresser_name_proximal <- paste(baseline_data$B13_hairdressername[baseline_data$B11a_phonenumber == j & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
      hairdresser_nickname_proximal <- paste(baseline_data$B13_hairdresser_nickname[baseline_data$B11a_phonenumber == j & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
      hairdresser_location_proximal <- paste(baseline_data$B14_hairdresserlocation[baseline_data$B11a_phonenumber == j & !is.na(baseline_data$B11a_phonenumber)], collapse = "\n")
      final_ids_proximal <- paste(baseline_data$final_ID[baseline_data$B11a_phonenumber == j & !is.na(baseline_data$B11a_phonenumber)], collapse = ", ")
      
      # Compile a new row to add to the dataframe to aid identification of typos
      temp_data1 <- data.frame(Source_Phonenumber = i,
                               Source_Information = paste0("N = ",freq_source, "\n",
                                                           "Cluster ID: ", paste0(cluster_id_source, collapse = ", "), "\n",
                                                           "Hairdresser Name: ", paste0(hairdresser_name_source, collapse = ", "), "\n",
                                                           "Hairdresser Nickname: ", paste0(hairdresser_nickname_source, collapse = ", "), "\n",
                                                           "\nHairdresser Location:\n", paste0(hairdresser_location, collapse = "\n")),
                             Source_IDs = final_ids_source,
                             Proximal_Phonenumber = proximal_phone_numbers[count_2], 
                             Proximal_Information = paste0("N = ", freq_proximal[count_2], "\n",
                                                           "Proximity: ", phone_numbers_proximity[count_2], "\n",
                                                           "Cluster ID: ", paste0(cluster_id_proximal, collapse = ", "), "\n",
                                                           "Hairdresser Name: ", paste0(hairdresser_name_proximal, collapse = ", "), "\n",
                                                           "Hairdresser Nickname: ", paste0(hairdresser_nickname_proximal, collapse = ", "), "\n",
                                                           "\nHairdresser Location:\n", paste0(hairdresser_location_proximal, collapse = "\n")),
                             Proximal_IDs = final_ids_proximal)
      
      suspected_typos_df <- rbind(suspected_typos_df, temp_data1)
      
      count_2 <- count_2 + 1
    }
  }
}

#range_write(suspected_typos_df, 
#            ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=1106637800",
#            sheet = "Detecting Phone Number Typos",
#            range = "A2",
#            col_names = F,
#            reformat = F)

```

##### 6.1 Fix

```{r}

# There is one hairdresser which has two phone numbers but respondents going there have all just filled one. The code below fixes that.
baseline_data$B12a_alternativepn[baseline_data$final_ID %in% c("54168Dec8102822", "64185Dec8121511", "87125Dec12120750", "73118Dec12144407")] <- 104503182
baseline_data$B11a_phonenumber[baseline_data$final_ID %in% c("89177Nov30125223")] <- 724503182
baseline_data$B11a_phonenumber_double[baseline_data$final_ID %in% c("89177Nov30125223")] <- 724503182
baseline_data$B12a_alternativepn[baseline_data$final_ID %in% c("89177Nov30125223")] <- 104503182

# There is one hairdresser that upon confirming a typo gave us 2 phone numbers. Code below adds the second as an alternative phone number
baseline_data$B12a_alternativepn[baseline_data$final_ID %in% c("106181Nov20112523")] <- 0711498982

```

```{r}

# First remove all phone number entries that contain 7000000
baseline_data[baseline_data$B11a_phonenumber == "700000000" & !is.na(baseline_data$B11a_phonenumber),]$B11_phonenumber_check <- 0
baseline_data[baseline_data$B11a_phonenumber == "700000000" & !is.na(baseline_data$B11a_phonenumber),]$B11a_phonenumber_double <- NA
baseline_data[baseline_data$B11a_phonenumber == "700000000" & !is.na(baseline_data$B11a_phonenumber),]$B11a_phonenumber <- NA

```


```{r}
typo_detection_sheet <- read_sheet(ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=1106637800",
                                   sheet = "Detecting Phone Number Typos")
colnames(typo_detection_sheet)[10] <- "correct_phone_number_source"
colnames(typo_detection_sheet)[11] <- "correct_phone_number_proximal"

# Replace "None" with NA
typo_detection_sheet$correct_phone_number_source[which(typo_detection_sheet$correct_phone_number_source == "None")] <- NA
typo_detection_sheet$correct_phone_number_proximal[which(typo_detection_sheet$correct_phone_number_proximal == "None")] <- NA


# Go through the sheet and replace the relevant numbers
for(i in 1:nrow(typo_detection_sheet)){
  
  if(typo_detection_sheet$Judgement[i] == "Independent Numbers"){
    
    next
    
  } else if(typo_detection_sheet$Judgement[i] == "Both have a Typo"){
    
    baseline_data$B11a_phonenumber[baseline_data$final_ID %in% str_split(typo_detection_sheet$Source_IDs, ", ")[[i]]] <- typo_detection_sheet$correct_phone_number_source[[i]]
    
    baseline_data$B11a_phonenumber[baseline_data$final_ID %in% str_split(typo_detection_sheet$Proximal_IDs, ", ")[[i]]] <- typo_detection_sheet$correct_phone_number_proximal[[i]]
    
  } else if(typo_detection_sheet$Judgement[i] == "Source has a Typo"){
    
    baseline_data$B11a_phonenumber[baseline_data$final_ID %in% str_split(typo_detection_sheet$Source_IDs, ", ")[[i]]] <- typo_detection_sheet$correct_phone_number_source[[i]]
    
  } else if(typo_detection_sheet$Judgement[i] == "Proximal has a Typo"){
    
    baseline_data$B11a_phonenumber[baseline_data$final_ID %in% str_split(typo_detection_sheet$Proximal_IDs, ", ")[[i]]] <- typo_detection_sheet$correct_phone_number_proximal[[i]]
    
  }
}

```



### 7. Manually matching hairdressers based on locations that don't have phone numbers

```{r}

# Extract all IDs where no phone number for the hairdresser was provided

baseline_data[baseline_data$B11_phonenumber_check == 0 | is.na(baseline_data$B11a_phonenumber),] %>% 
  arrange(county_name, B0_cluster, submission_date_dateonly) %>% 
  dplyr::select(final_ID, en_name, county_name, B0_cluster, B13_hairdressername, B13_hairdresser_nickname, B14_hairdresserlocation) %>% 
  range_write(ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=0", 
              sheet = "Matching_Hairdressers_without_phonenumbers", 
              range = "A2", 
              col_names = F, 
              reformat = F)
  

# Upload all other responses to enable effective command+f work
baseline_data[baseline_data$B11_phonenumber_check == 1  | !is.na(baseline_data$B11a_phonenumber),] %>% 
  arrange(county_name, B0_cluster, submission_date_dateonly) %>% 
  dplyr::select(final_ID, en_name, county_name, B0_cluster, B13_hairdressername, B13_hairdresser_nickname, B14_hairdresserlocation) %>% 
  range_write(ss = "https://docs.google.com/spreadsheets/d/1L5oYnl6DeUabV-9v5cAKt_TOkfktLXX9l3tUHL9r6L8/edit#gid=0", 
              sheet = "Matching_Hairdressers_without_phonenumbers", 
              range = paste0("A",sum(baseline_data$B11_phonenumber_check == 0 | is.na(baseline_data$B11a_phonenumber))+3), 
              col_names = F, 
              reformat = F)


```


## Export

```{r}
# Export cleaned Data
write.csv(baseline_data, "Data Exports/vcf2_rct_baseline_caregivers_clean.csv")

test <- read.csv("Data Exports/vcf2_rct_baseline_caregivers_clean.csv")

```
